### 2016-09-23 rebuttal.tex

\subsection{Experimental design}
No Comments

\subsection{Validity of the findings}
\begin{questions}
\question There is a minor problem with the supplementary notebook

The final cell is

% This depends on matplotlib. We want to make sure the rest of the paper
% doesn't depend on it, so skip.
% no-doctest
\begin{verbatim}
>>> circuit_plot(fourier, nqubits=3);
plt.savefig('./images/circuitplot-qft.pdf', format='pdf')
\end{verbatim}

@@

\begin{solution}
We have added a citation for mpmath.
\end{solution}
\end{questions}

\section{Reviewer 3}

\begin{questions}
\question I suggest a major rewrite of the paper, to improve the structure and group differently approached subjects. It would probably be best to:
\begin{enumerate}
\item Create a new section (following the introduction of SymPy) on projects that use SymPy, and put in it the materials currently available in supplement's sections 8, 9, 11. The comparison with Mathematica (supplement's section 10) should be moved either to the introduction as a section, or right after the introduction as its own section, but it should not be in the middle of the description of SymPy-powered projects.
\item  This should be followed by the list of SymPy packages and modules (currently section 3) and descriptions of selected modules (currently sections 3.1, 3.3, 3.5, supplement's sections 5, 7, and 9).
\item Now, basic usage can be given as its own section (currently done in sections 2.1 and 2.3), followed by introductions on usage of various modules (currently in sections 3.2, 3.4, 3.6, 4, 5, and supplement's sections 2, 3, 4, 6).
\item In-depth architecture (most of the so far unmentioned sections) can be given either as its own section, or made into a supplement of its own (as it is naturally far more technical and less interesting to general audience).
\item The current conclusion works fine as the finishing section of the paper.
\end{enumerate}
\begin{solution}
  We have made the following changes to the paper

  \begin{enumerate}
  \item We have renamed the ``Features'' section to ``Overview of
    Capabilities''.
    \item We have renamed the ``Domain Specific Submodules'' section to
      ``Physics Submodule'' (see point~\ref{rev3point30}).
  \item We have moved the ``Architecture'' section to the end, after the
    ``Physics Submodule'' section.
  \item We have moved the ``Basic Usage'' subsection to the beginning of the
    ``Overview of Capabilities'' section, and added an intro paragraph to the
    ``Overview of Capabilities'' section.
  \item We have moved the ``Assumptions'' subsection to the ``Overview of
    Capabilities'' subsection, after the features table.
  \item The ``Comparison with Mathematica'' section has been moved to the end of
    the supplement.
  \end{enumerate}

We disagree with the reviewer on a few points. We do not consider SymPy Live
or SymPy Gamma to be key components of SymPy. The paper goal of the paper is
to be about the SymPy library. While SymPy Live and SymPy Gamma are
maintained by the SymPy community, they are separate projects. A
mention of SymPy Live has been added to the introduction (see editor
point~\ref{editorpoint1}), as it may assist an interested reader in trying the
examples from the paper.

### 2016-09-23 rebuttal.tex

We disagree with the reviewer on a few points. We do not consider SymPy Live
or SymPy Gamma to be key components of SymPy. The paper goal of the paper is
to be about the SymPy library. While SymPy Live and SymPy Gamma are
maintained by the SymPy community, they are separate projects. A
mention of SymPy Live has been added to the introduction (see editor
point~\ref{editorpoint1}), as it may assist an interested reader in trying the
examples from the paper.

The ``Other Projects that
Depend on SymPy'' section (which has been renamed from ``Other Projects that
Use SymPy'') is {\color{red}TODO: Add reasons here, or else move this to the
paper as the reviewer requests.}

The ``Comparison with Mathematica'' section has been placed in the supplement
because we do not feel that a treatment in the main manuscript would be fair
without an equal comparison to other principle computer algebra systems, such
as Maple, SageMath, and Maxima. Unfortunately, our authorship is inexpert in
these systems, so a complete and fair comparison is impossible.

We deem all the sections in section 3 (now section 2) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively---only set sets module is potentially applicable to the wider
audience of the main paper. However, in SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}. The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. We consider
the module too niche to warrant expanding upon in the main manuscript. SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.

@@

\question In lines 543 and 545, ``rad'' should be removed. Radians are assumed when no other measure (like degrees) is given.
\begin{solution}
These units were removed.
\end{solution}

\question In lines 567--568, ``performing symbolic quantum mechanics'' makes no sense. This should probably be ``computations'', ``solving problems related to'', etc.
\begin{solution}
This was reworded to:
\begin{quote}
to solve problems in quantum mechanics
\end{quote}
\end{solution}

\question The sentence ``SymPy expressions are immutable trees of Python objects.'' doesn't belong in the conclusion. This can be moved to the appropriate place when discussing SymPy's architecture.
\begin{solution}
This paper focuses on the architecture of SymPy, and we consider this to be a
core feature of SymPy's architecture, hence, it's inclusion in the conclusion.
We have also discussed the different points in this sentence in-depth in the architecture section.
\end{solution}

\question All ``submodules'' should be replaced by ``modules'' (examples:
lines 657, 662).
\label{rev1point37}
\begin{solution}
  Our use of ``modules'', ``submodules'', and ``packages'' coincides with the
  definitions used in the official Python documentation (see
  \url{https://docs.python.org/3/tutorial/modules.html#packages} and
  \url{https://docs.python.org/3/glossary.html#term-package}). The distinction
  between (sub)module and (sub)package in terms of Python libraries seems very
  technical. To clarify things, we have modified the manuscript to use
  ``package'' only when referring to a library external to SymPy (such as
  mpmath and Xy-pic).

### 2016-09-23 rebuttal.tex

The authors

\pagebreak

\section{Comments from Editor}

\begin{questions}
\question I found the \url{http://live.sympy.org/} site very convenient for trying things
out in SymPy, but it is only mentioned in the supplement, which might be
overlooked by readers. I suggest moving that section into the main paper, as
it provides a great way to play along with the examples while reading the
paper.
\begin{solution}
\label{editorpoint1}
This sentence was added to the introduction:
\begin{quote}
All examples could be tested on the \href{http://live.sympy.org}{SymPy
Live} instance, that is an online Python shell, which uses the Google
App Engine to execute SymPy code.
\end{quote}
\end{solution}
\question The Basic Usage section omits what I think is an important point:
how does one distinguish between evaluating exp(1) in Python and exp(1) in
SymPy? In other words, how are symbolic constants specified?
\begin{solution}
  Both Python standard library and SymPy have exp callable, so it depends
  which symbols are imported in your global namespace: the \texttt{exp}
  function from the \texttt{math} module or the \texttt{exp} class from SymPy.
  In the later case a special symbolic constant will be produced.

@@

  \begin{enumerate}
  \item We have renamed the ``Features'' section to ``Overview of
    Capabilities''.
    \item We have renamed the ``Domain Specific Submodules'' section to
      ``Physics Submodule'' (see point~\ref{rev3point30}).
  \item We have moved the ``Architecture'' section to the end, after the
    ``Physics Submodule'' section.
  \item We have moved the ``Basic Usage'' subsection to the beginning of the
    ``Overview of Capabilities'' section, and added an intro paragraph to the
    ``Overview of Capabilities'' section.
  \item We have moved the ``Assumptions'' subsection to the ``Overview of
    Capabilities'' subsection, after the features table.
  \item The ``Comparison with Mathematica'' section has been moved to the end of
    the supplement.
  \end{enumerate}

We disagree with the reviewer on a few points. We do not consider SymPy Live
or SymPy Gamma to be key components of SymPy. The paper goal of the paper is
to be about the SymPy library. While SymPy Live and SymPy Gamma are
maintained by the SymPy community, they are separate projects. A
mention of SymPy Live has been added to the introduction (see editor
point~\ref{editorpoint1}), as it may assist an interested reader in trying the
examples from the paper.

% TODO For projects that use SymPy
% TODO: Make intro sentence longer.
% TODO: Make it into a table
% TODO: Project name, domain, description

### 2016-09-23 rebuttal.tex

% TODO For projects that use SymPy
% TODO: Make intro sentence longer.
% TODO: Make it into a table
% TODO: Project name, domain, description

The ``Other Projects that
Depend on SymPy'' section (which has been renamed from ``Other Projects that
Use SymPy'') is {\color{red}TODO: Add reasons here, or else move this to the
paper as the reviewer requests.}

The ``Comparison with Mathematica'' section has been placed in the supplement
because we do not feel that a treatment in the main manuscript would be fair
without an equal comparison to other principle computer algebra systems, such
as Maple, SageMath, and Maxima. Unfortunately, our authorship is inexpert in
these systems, so a complete and fair comparison is impossible.

We deem all the sections in section 3 (now section 2) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively---only the sets module is potentially applicable to the wider
audience of the main paper. However, in SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}. The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. We consider
the module too niche to warrant expanding upon in the main manuscript. SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.

### 2016-09-23 rebuttal.tex

% TODO For projects that use SymPy
% TODO: Make intro sentence longer.
% TODO: Make it into a table
% TODO: Project name, domain, description

The ``Other Projects that
Depend on SymPy'' section (which has been renamed from ``Other Projects that
Use SymPy'') is {\color{red}TODO: Add reasons here, or else move this to the
paper as the reviewer requests.}

The ``Comparison with Mathematica'' section has been placed in the supplement
because we do not feel that a treatment in the main manuscript would be fair
without an equal comparison to other principle computer algebra systems, such
as Maple, SageMath, and Maxima. Unfortunately, our authorship is inexpert in
these systems, so a complete and fair comparison is impossible.

We deem all the sections in section 3 (now section 2) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively:
\begin{itemize}
\item In SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}.

\item The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. We consider
the module too niche to warrant expanding upon in the main manuscript.

\item SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.
\end{itemize}

### 2016-09-23 rebuttal.tex

We deem all the sections in section 3 (now section 2) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively:
\begin{itemize}
\item In SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}.

\item The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. We consider
the module too niche to warrant expanding upon in the main manuscript.

\item SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript. The
``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.
The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the logic module discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the future
work section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

### 2016-09-23 rebuttal.tex

We deem all the sections in section 3 (now section 2) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively:
\begin{itemize}
\item In SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}.

\item The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. We consider
the module too niche to warrant expanding upon in the main manuscript.

\item SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript.

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the logic module discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the future
work section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

\item The ``Solvers'' subsection already mentions that SymPy can solve Diophantine
equations. We consider this specific application to be niche enough to keep
the discussion in the supplement. We have added a reference to the supplement
to the ``Solvers'' subsection.

\item The ``Statistics'' module is an independent
submodule (no other SymPy submodules depend on it). We do not consider it to
be a core module of SymPy.
\end{itemize}

### 2016-09-23 rebuttal.tex

\item SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript.

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the future
work section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

### 2016-09-23 rebuttal.tex

\item SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript.

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the
``Conclusion and Future
Work'' section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

### 2016-09-23 rebuttal.tex

\item SymPy
Live, as has been discussed above, is not a SymPy submodule. It is a separate
project from the SymPy library. It would be inappropriate to list it alongside
the features of SymPy.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript.

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

% TODO: Note that old assumptions do not use sympy.logic
% TODO: Reference the RETE algorithm
\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the
``Conclusion and Future
Work'' section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

\item Regarding the ``Diophantine Solvers'' section, the ``Solvers''
  subsection already mentions that SymPy can solve Diophantine Equations. This
  is outside of the scope of the paper, because it's too specific. We have
  added a reference to the supplement to the ``Solvers'' subsection.

### 2016-09-23 rebuttal.tex

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript.

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

% TODO: Note that old assumptions do not use sympy.logic
% TODO: Reference the RETE algorithm
\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the
``Conclusion and Future
Work'' section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

\item Regarding the ``Diophantine Solvers'' section, the ``Solvers''
  subsection already mentions that SymPy can solve Diophantine Equations. This
  is outside of the scope of the paper, because it's specific, and mostly
  independent from other parts of SymPy. We have
  added a reference to the supplement to the ``Solvers'' subsection.

### 2016-09-23 rebuttal.tex

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript.

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

% TODO: Note that old assumptions do not use sympy.logic
% TODO: Reference the RETE algorithm
\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the
``Conclusion and Future
Work'' section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

\item Regarding the ``Diophantine Solvers'' section, the ``Solvers''
  subsection already mentions that SymPy can solve Diophantine Equations. The
  in depth discussion in the supplement
  is outside of the scope of the main paper, because it's specific, and
  independent from parts of SymPy (with the exception of computing integer set
  intersections in the \texttt{sympy.sets} submodule, no other part of SymPy
  from solvers uses the Diophantine solvers). We have
  added a reference to the supplement to the ``Solvers'' subsection.

### 2016-09-23 rebuttal.tex

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript.

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

% TODO: Note that old assumptions do not use sympy.logic
% TODO: Reference the RETE algorithm
\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the
``Conclusion and Future
Work'' section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

\item Regarding the ``Diophantine Solvers'' section, the ``Solvers''
  subsection already mentions that SymPy can solve Diophantine Equations. The
  in depth discussion in the supplement
  is outside of the scope of the main paper, because it's specific, and
  independent from other parts of SymPy (with the exception of computing integer set
  intersections in the \texttt{sympy.sets} submodule, no other part of SymPy
  from solvers uses the Diophantine solvers). We have
  added a reference to the supplement to the ``Solvers'' subsection.

### 2016-09-23 rebuttal.tex

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

% TODO: Note that old assumptions do not use sympy.logic
% TODO: Reference the RETE algorithm
\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the
``Conclusion and Future
Work'' section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

\item Regarding the ``Diophantine Solvers'' section, the ``Solvers''
  subsection already mentions that SymPy can solve Diophantine Equations. The
  in depth discussion in the supplement
  is outside of the scope of the main paper, because it's specific, and
  independent from other parts of SymPy (with the exception of computing integer set
  intersections in the \texttt{sympy.sets} submodule, no other part of SymPy
  from solvers uses the Diophantine solvers). We have
  added a reference to the supplement to the ``Solvers'' subsection.

\item The ``Statistics'' module is not a core module and is independent (no
  other SymPy submodules depend on it).
\end{itemize}

The architecture is one of the most important parts of the paper. The goal of
the paper is to discuss the architecture core features of SymPy. We therefore
strongly feel that this section belongs in the main manuscript, and not the
supplementary material. We have followed the reviewer's advice and moved the
architecture section to the end of the paper, to make the paper easier to
follow.
\end{solution}
\end{questions}

### 2016-09-23 rebuttal.tex

% TODO: Note that old assumptions do not use sympy.logic
% TODO: Reference the RETE algorithm
\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the \texttt{sympy.logic} submodule discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the
``Conclusion and Future
Work'' section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

\item Regarding the ``Diophantine Solvers'' section, the ``Solvers''
  subsection already mentions that SymPy can solve Diophantine Equations. The
  in depth discussion in the supplement
  is outside of the scope of the main paper, because it's specific, and
  independent from other parts of SymPy (with the exception of computing integer set
  intersections in the \texttt{sympy.sets} submodule, no other part of SymPy
  from solvers uses the Diophantine solvers). We have
  added a reference to the supplement to the ``Solvers'' subsection.

\item The ``Statistics'' module is not a core module and is independent (no
  other SymPy submodules depend on it).
\end{itemize}

The ``Architecture'' section is a key component of the paper. The goal of the
paper is to discuss the architecture and core features of SymPy. It therefore
would be inappropriate to move this section to the supplement. We have
followed the reviewer's advice and moved the architecture section to the end
of the paper, to make the paper easier to follow.
\end{solution}
\end{questions}

### 2016-09-23 rebuttal.tex

\unframedsolutions
\shadedsolutions
\renewcommand{\solutiontitle}{}

\begin{document}

Dear Editors, \bigskip

We thank you and the referees for your most helpful comments and suggestions
on our manuscript, ``SymPy: Symbolic Computing in Python''.
The manuscript is greatly improved as a result.

Below we give your and the reviewers' comments on white background and our
replies on gray background. \bigskip

### 2016-09-23 rebuttal.tex

\unframedsolutions
\shadedsolutions
\renewcommand{\solutiontitle}{}

\begin{document}

Dear Editors, \bigskip

We thank you and the referees for your thoughtful comments and suggestions on
our manuscript, ``SymPy: Symbolic Computing in Python''. The manuscript is
greatly improved as a result. We have endeavored to address your comments and
concerns point by point below. Below we give your and the reviewers' comments
on white background and our replies on gray background. \bigskip

Reviewer 1 had concerns that the paper was out of scope, but the editor has
confirmed that it is in scope. Many of the points that reviewer 3 raised were
in regards to the relevance of various sections. The intended scope of this
paper was to be an architecture paper for SymPy's 1.0 release. We have
examined reviewer 3's points through this lens. In light of this, which
contents were previously in the supplement vs.\ the main manuscript was
confusing. To address this, we have made some restructurings of the
manuscript, to make the paper more clear to a general audience.

### 2016-09-23 rebuttal.tex

\unframedsolutions
\shadedsolutions
\renewcommand{\solutiontitle}{}

\begin{document}

Dear Editors, \bigskip

We thank you and the referees for your thoughtful comments and suggestions on
our manuscript, ``SymPy: Symbolic Computing in Python''. We have endeavored to
address your comments and concerns point by point below. Below we give your
and the reviewers' comments on white background and our replies on gray
background. \bigskip

Reviewer 1 had concerns that the paper was out of scope, but the editor has
confirmed that it is in scope. Many of the points that reviewer 3 raised were
in regards to the relevance of various sections. The intended scope of this
paper was to be an architecture paper for SymPy's 1.0 release. We have
examined reviewer 3's points through this lens. In light of this, which
contents were previously in the supplement vs.\ the main manuscript may have
been confusing to a general audience. To address this, we have restructured
the manuscript to make the paper more readable to those not already experts in
SymPy or symbolic mathematics. \bigskip

### 2016-09-23 other_projects_that_use_sympy.tex
Add SymPy Live and SymPy Gamma to the projects that depend on SymPy section

\begin{itemize}
\item
  \href{http://cadabra.science/index.html}{\textbf{Cadabra}}: Cadabra is
  a CAS designed specifically for the
  resolution of problems encountered in field theory.
\item
  \href{http://octave.sourceforge.net/symbolic/}{\textbf{Octave Symbolic}}:
  The Octave-Forge Symbolic package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features.
\item
  \href{https://github.com/jverzani/SymPy.jl}{\textbf{SymPy.jl}}:
  Provides a Julia interface to SymPy using PyCall.
\item
  \href{https://mathics.github.io/}{\textbf{Mathics}}: Mathics is a
  free, general-purpose online CAS featuring Mathematica compatible
  syntax and functions. It is backed by highly extensible Python code,
  relying on SymPy for most mathematical tasks.
\item
  \href{http://mathpix.com/}{\textbf{Mathpix}}: An iOS App, that detects handwritten math as input, and uses
  SymPy Gamma to evaluate the math input and generate the relevant
  steps to solve the problem.
\item
  \href{http://openrave.org/docs/0.8.2/openravepy/ikfast/}{\textbf{IKFast}}:
  IKFast is a robot kinematics compiler provided by
  \href{http://openrave.org/}{OpenRAVE}. It analytically solves robot inverse
  kinematics equations and generates optimized C++ files. It uses SymPy for
  its internal symbolic mathematics.
\item
  \href{http://www.sagemath.org/}{\textbf{Sage}}: A CAS, visioned to be
  a viable free open source alternative to Magma, Maple, Mathematica and
  MATLAB\@. Sage includes many open source mathematical libraries, including
  SymPy.
\item
  \href{https://cloud.sagemath.com}{\textbf{SageMathCloud}}:
  SageMathCloud is a web-based cloud computing and course management
  platform for computational mathematics.
\item
  \href{http://www.pydy.org/}{\textbf{PyDy}}: Multibody Dynamics with
  Python.
\item
  \href{https://github.com/brombo/galgebra}{\textbf{galgebra}}:
  Geometric algebra (previously \texttt{sympy.galgebra}).
\item
  \href{http://yt-project.org/}{\textbf{yt}}: Python package for
  analyzing and visualizing volumetric data (\texttt{yt.units} uses SymPy).
\item
  \href{http://sfepy.org/}{\textbf{SfePy}} (Simple finite elements in Python),
  cf.~\cite{cimrman2014sfepy}, is a Python package for solving partial
  differential equations (PDEs) in 1D, 2D and 3D by the finite element (FE)
  method~\cite{Zienkiewicz2013FEM}. SymPy is used within this package mostly for
  code generation and testing.
\item
  \href{http://quameon.sourceforge.net/}{\textbf{Quameon}}: Quantum
  Monte Carlo in Python.
\item
  \href{http://lcapy.elec.canterbury.ac.nz/}{\textbf{Lcapy}}:
  Experimental Python package for teaching linear circuit analysis.
\end{itemize}

>>>>

\begin{itemize}
\item SymPy Live: SymPy Live an online Python shell, which uses the Google
App Engine to executes SymPy code. It is integrated in the SymPy
documentation examples at \href{http://docs.sympy.org}{http://docs.sympy.org}.
SymPy Live is maintained by the SymPy community.
\item SymPy Gamma: SymPy Gamma is a web application that executes and displays
  results for SymPy expressions, in a fashon similar to that of Wolfram|Alpha.
  SymPy Gamma is maintained by the SymPy community.
  See the supplementary material for more information about SymPy Gamma.
\item
  \href{http://cadabra.science/index.html}{\textbf{Cadabra}}: Cadabra is
  a CAS designed specifically for the
  resolution of problems encountered in field theory.
\item
  \href{http://octave.sourceforge.net/symbolic/}{\textbf{Octave Symbolic}}:
  The Octave-Forge Symbolic package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features.
\item
  \href{https://github.com/jverzani/SymPy.jl}{\textbf{SymPy.jl}}:
  Provides a Julia interface to SymPy using PyCall.
\item
  \href{https://mathics.github.io/}{\textbf{Mathics}}: Mathics is a
  free, general-purpose online CAS featuring Mathematica compatible
  syntax and functions. It is backed by highly extensible Python code,
  relying on SymPy for most mathematical tasks.
\item
  \href{http://mathpix.com/}{\textbf{Mathpix}}: An iOS App, that detects handwritten math as input, and uses
  SymPy Gamma to evaluate the math input and generate the relevant
  steps to solve the problem.
\item
  \href{http://openrave.org/docs/0.8.2/openravepy/ikfast/}{\textbf{IKFast}}:
  IKFast is a robot kinematics compiler provided by
  \href{http://openrave.org/}{OpenRAVE}. It analytically solves robot inverse
  kinematics equations and generates optimized C++ files. It uses SymPy for
  its internal symbolic mathematics.
\item
  \href{http://www.sagemath.org/}{\textbf{Sage}}: A CAS, visioned to be
  a viable free open source alternative to Magma, Maple, Mathematica and
  MATLAB\@. Sage includes many open source mathematical libraries, including
  SymPy.
\item
  \href{https://cloud.sagemath.com}{\textbf{SageMathCloud}}:
  SageMathCloud is a web-based cloud computing and course management
  platform for computational mathematics.
\item
  \href{http://www.pydy.org/}{\textbf{PyDy}}: Multibody Dynamics with
  Python.
\item
  \href{https://github.com/brombo/galgebra}{\textbf{galgebra}}:
  Geometric algebra (previously \texttt{sympy.galgebra}).
\item
  \href{http://yt-project.org/}{\textbf{yt}}: Python package for
  analyzing and visualizing volumetric data (\texttt{yt.units} uses SymPy).
\item
  \href{http://sfepy.org/}{\textbf{SfePy}} (Simple finite elements in Python),
  cf.~\cite{cimrman2014sfepy}, is a Python package for solving partial
  differential equations (PDEs) in 1D, 2D and 3D by the finite element (FE)
  method~\cite{Zienkiewicz2013FEM}. SymPy is used within this package mostly for
  code generation and testing.
\item
  \href{http://quameon.sourceforge.net/}{\textbf{Quameon}}: Quantum
  Monte Carlo in Python.
\item
  \href{http://lcapy.elec.canterbury.ac.nz/}{\textbf{Lcapy}}:
  Experimental Python package for teaching linear circuit analysis.
\end{itemize}
